A data-intensive assessment of the species-abundance distribution.

### 2015-02-13 defense_pres.tex
Makes title larger by making the font size smaller through some magic I do not fully comprehend.

\documentclass[20pt]{beamer}
\usetheme{Pittsburgh}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Elita Baldridge}
\title{A data-intensive assessment of the species-abundance distribution.
}
%\setbeamercovered{transparent} 
%\logo{} 
%\institute{} 
%\subject{} 
\begin{document}

>>>>

\documentclass[20pt]{beamer}
\usetheme{Pittsburgh}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Elita Baldridge}
\title{A data-intensive assessment of the species-abundance distribution.}
\setbeamertemplate{navigation symbols}{}
\date{}
%\setbeamercovered{transparent} 
%\logo{\includegraphics[scale=.03]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.07]{../Miscellaneous/Pictures/Weecology.png}} 
\institute{\includegraphics[scale=.03]{../Miscellaneous/Pictures/ecology_center_horizontal.jpg}\includegraphics[scale=0.07]{../Miscellaneous/Pictures/Weecology.png}} 
%\subject{} 
\begin{document}
